---
title: "Exercise"
output:
  html_document:
    df_print: paged
---

```{r, setup, include=F}
require(tidyverse)
```

# Introduction

The exercise consists of applying NLP to find similar text.

Data is taken from [this](http://help.sentiment140.com/for-students/) open source dataset for NLP analysis. You can download the zipped dataset directly [here](https://docs.google.com/file/d/0B04GJPshIjmPRnZManQwWEdTZjg/edit?resourcekey=0-betyQkEmWZgp8z0DFxWsHw).

Feel free to use R or Python (I am primarily an R user).

# Data load

Let's have a look at the dataset:

```{r, cache=T}
data <- readr::read_csv("./trainingandtestdata/training.1600000.processed.noemoticon.csv", col_names = F)
data <- data %>% stats::setNames(c("Polarity", "ID", "Date", "Query", "User", "Text"))
data %>% head()
```

# Exercise description

Retrieve the 10 most similar tweets to the following tweet text:

```{r}
data %>% filter(ID == "1467810672") %>% select("Text")
```

If your computer has issues to handle the size of the data, feel free to limit it.

Tips:

- Start simple
- Show reasoning

Extra (optional): 

- Call the function via an API call 
- Make the most basic front-end to call the API
